\newpage
\parindent=1cm %красная строка
\addcontentsline{toc}{section}{Список литературы} %Убираем номер , даём имя в оглавлении 

%http://fkn.ktu10.com/?q=node/6860

\begin{thebibliography}{}
	\bibitem{Handber:2015} R. Handberg. <<The symbolic politics of ballistic missile defense: seeking the perfect defense in an imperfect world>>. Defense and Security Analysis 31(1), 44 – 58, 2015.
	\bibitem{Marshall:2013} E. Marshall. <<A midcourse correction for U.S. missile defense	system>>. Science 339(6127), 1508 – 1511, 2013.
	\bibitem{Ganguly:2014} S. Ganguly. <<India’s pursuit of ballistic missile defense>>. The	Nonproliferation Review21(3/4),  373 -380, 2014.
	\bibitem{Nguyen:2014} U. B. Nguyen. <<Assessment of a ballistic missile defense system>>. Defense and Security Analysis  30(1), 4 – 17, 2014.
	\bibitem{Armstrong:2014} M. J. Armstrong. <<Modeling short-range ballistic missile defense and Israel’s iron dome system>>. Operations Research, 62(5), 1028 – 1040, 2014.
	\bibitem{Sommerer:2012} S. Sommerer, M. D. Guevara, M. A. Landis, et al. <<Systems-ofsystems engineering in air and missile defense>>. John Hopkins
	APL Technical 31(1), 5 – 20, 2012.
	\bibitem{Cheng:2015}  Z. L. Cheng, L. Fan, Y. L. Zhang. <<A framework for equipment systems-of-systems effectiveness evaluation using parallel experiments approach>>. Journal of Systems Engineering and	Electronics 26(2), 292 – 300, 2015.
	\bibitem{Holland:2006} J. H. Holland. <<Studying complex adaptive systems>>. Journal of	System Science and Complexity 19, 1 – 8, 2006.
	\bibitem{Macal:2010} C. M. Macal, M. J. North. <<Tutorial on agent-based modeling
	and simulation>>. Journal of Simulation, 2010 4(3): 151 – 162.
	\bibitem{Holland:2011} O. T. Holland, S. E. Wallace. <<Using agents to model the kill
	chain of the ballistic missile defense system>>. Naval Engineer 	Journal, 123(3), 141 – 151, 2011.
	\bibitem{Lynch:2013}  C. J. Lynch, S. Y. Diallo, A. Tolk. <<Representing the ballistic 	missile defense system using agent-based modeling>>. Proc. of
	the Military Modeling and Simulation Symposium, 1 – 8, 2013.
	\bibitem{Connors:2015}  C. D. Connors, J. O. Miller, B. J. Lunday. <<Using agent-based	modeling and a designed experiment to simulate and analyze a	new air-to-air missile >>. The Journal of Defense Modeling and	Simulation: Applications, Methodology, Technology 12(5), 1 – 10, 2015.
	\bibitem{Bui:1999}  T. Bui, J. Le. << An agent-based framework for building decision support systems >>. Decision Support Systems 25(3),	225 – 237, 1999.
	\bibitem{Li:2015} L. Y. Li, F. X. Liu, G. Z. Long, et al. <<Modified particle swarm
	optimization for BMDS interceptor resource planning>>. Applied
	Intelligence  43(2), 1 – 18, 2015.
	\bibitem{Wooldridge:2002} M. Wooldridge. <<An introduction to multi agent systems>>. Chichester: John Wiley \& Sons, 2002.
	\bibitem{Gooding:1990} R. H. Gooding. <<A procedure for the solution of Lambert’s orbital boundary-value problem>>. Celestial Mechanics and Dynamical Astronomy  (48), 145 – 165, 1990.
	\bibitem{Kondratiev:2010}  Кондратьев М. А.,	Ивановский Р. И.,	Цыбалова Л.М. Применение агентного подхода к имитационному моделированию процесса распространения заболевания / М.А. Кондратьев, Ивановский Р.И., Цыбалова Л.М. // Научно-технические ведомости СПбГПУ. Физико-математические науки. 2010. № 2. - С. 189–194.
	
	\bibitem{Eberhart:1995} R. Eberhart, J. Kennedy. A new optimizer using particle swarm	theory. Proc. of the Sixth International Symposium on MicroMachine and Human Science,  39 – 43, 1995.
	\bibitem{Cheng:2017} Zilong Cheng, Li Fan, Yulin Zhang. <<Multi-agent decision support system for missile defense based on improved PSO algorithm>>.   Journal of Systems Engineering and Electronics Vol. 28, No. 3,  514 – 525, 2017.
	\bibitem{websockets:git} Library for building WebSocket servers and clients in Python. GitHub [Электронный ресурс] / Режим доступа: https://github.com/aaugustin/websockets
	
	
\end{thebibliography}